State of the Practice of Lattice Boltzmann Method Software Development

### 2021-07-27 StateOfPractice/Peter-Notes/Report/Report.tex
updated LBM report, split section 4

\noindent\textbf{NUMBER OF PAGES:} 119

@@

\begin{itemize}
	\item \textbf{Introduction} to the report, including its purpose, motivation, scope, and organization.
	\item LBM software \textbf{Domain Analysis}. A domain analysis consists of systematically identifying and documenting the commonalities, variabilities, and terminology of a software family \citep{Weiss1997}.
	The purpose of this analysis in this state of the practice assessment is to better classify the different software products based on their functionality.
	\item \textbf{Methodology} of this state of the practice assessment, including the steps of the methodology, software quality definitions and how these qualities are assessed in this report, an overview of candidate software selection, empirical measures gathered, and the AHP. This follows a general methodology for assessing the state of the practice for SCS domains.
	\item Quantitative and qualitative \textbf{Results}. 
	\item An analysis of the results and \textbf{Answers To Research Questions}.
	\item \textbf{Conclusion} to the report including comments on suggestions for future state of the practice assessments.
	\item \textbf{Appendix}: This section includes our Research Questions, the Measurement Template, Grading Template, Ethics Approval, and Developer Interview Questions.
\end{itemize}

@@

Software quality attributes facilitate the measurement and comparison of software packages in this state of the practice assessment. We adopt software quality definitions from various researchers and subject matter expert entities. Some of the definitions are from \cite{Smithetal2020}. The quality measurement results are found in Section \ref{qualityresults} of this report. Section \ref{qualityrecommentations} lists recommendations to address software qualities in LBM software packages. The following are the software quality definitions used in this state of the practice exercise, along with comments regarding their quantitative and qualitative measurement.

@@

\newpage
\section{Results}\label{qualityresults}

This section presents the quantitative and qualitative findings from data that was gathered for each quality listed in Section \ref{softwarequalities}. Quantitative results are presented in Section \ref{AHPresults}, and qualitative results are presented in Section \ref{interviewresults}.

\subsection{Quantitative Findings and AHP Results}\label{AHPresults}

This subsection presents the quantitative findings from data that was gathered using the measurement template found in Section \ref{measurementtemplate2}. The results of the AHP analysis based on that data are also presented in this subsection.

@@

@@

@@

@@

@@

@@

@@

\subsubsection{Reusability}\label{reusabilityresults}

@@

@@

@@

\subsubsection{Overall Quality}

@@

\subsection{Qualitative Findings From Developer Interviews}\label{interviewresults}

This subsection presents the qualitative findings from data that was gathered during interviews with developers. The interview questions are found in Appendix \ref{interviewquestions}.

@@

@@

@@

@@

@@

This section answers the research questions listed in Section \ref{purpose} using the quantitative and qualitative data presented in Section \ref{qualityresults}, additional data from software package repositories and artifacts, and domain expert feedback. Each subsection answers one of the research questions. Software package artifacts are examined in Section \ref{artifacts}, tools are listed in Section \ref{tools}, development principles, processes, and methodologies are discussed in Section \ref{prinprocmeth}, development pain points are explored in Section \ref{painpoints}, and our recommendations for improving software qualities are presented in Section \ref{qualityrecommentations}. A comparison between our designations of the software packages to community rankings is made in Section \ref{comparison}. Finally, threats to the validity of this assessment are noted in Section \ref{threats}.

>>>>

\noindent\textbf{NUMBER OF PAGES:} 120

@@

\begin{itemize}
	\item \textbf{Introduction} to the report, including its purpose, motivation, scope, and organization.
	\item LBM software \textbf{Domain Analysis}. A domain analysis consists of systematically identifying and documenting the commonalities, variabilities, and terminology of a software family \citep{Weiss1997}.
	The purpose of this analysis in this state of the practice assessment is to better classify the different software products based on their functionality.
	\item \textbf{Methodology} of this state of the practice assessment, including the steps of the methodology, software quality definitions and how these qualities are assessed in this report, an overview of candidate software selection, empirical measures gathered, and the AHP. This follows a general methodology for assessing the state of the practice for SCS domains.
	\item \textbf{Quantitative Results}. 
	\item \textbf{Qualitative Results}. 
	\item An analysis of the results and \textbf{Answers To Research Questions}.
	\item \textbf{Conclusion} to the report including comments on suggestions for future state of the practice assessments.
	\item \textbf{Appendix}: This section includes our Research Questions, the Measurement Template, Grading Template, Ethics Approval, and Developer Interview Questions.
\end{itemize}

@@

Software quality attributes facilitate the measurement and comparison of software packages in this state of the practice assessment. We adopt software quality definitions from various researchers and subject matter expert entities. Some of the definitions are from \cite{Smithetal2020}. The quality measurement results are found in Section \ref{AHPresults} of this report. Section \ref{qualityrecommentations} lists recommendations to address software qualities in LBM software packages. The following are the software quality definitions used in this state of the practice exercise, along with comments regarding their quantitative and qualitative measurement.

@@

\section{Quantitative Findings and AHP Results}\label{AHPresults}

This section presents the quantitative findings from data that was gathered using the measurement template found in Section \ref{measurementtemplate2} for qualities listed in Section \ref{softwarequalities}. The results of the AHP analysis based on that data are also presented in this section.

\subsection{Installability}

@@

\subsection{Surface Correctness and Verifiability}

@@

\subsection{Surface Reliability}

@@

\subsection{Surface Robustness}

@@

\subsection{Surface Performance}

@@

\subsection{Surface Usability}

@@

\subsection{Maintainability}

@@

\subsection{Reusability}\label{reusabilityresults}

@@

\subsection{Surface Understandability}

@@

\subsection{Visibility and Transparency}

@@

\subsection{Overall Quality}

@@

\section{Qualitative Findings From Developer Interviews}\label{interviewresults}

This section presents the qualitative findings from data that was gathered during interviews with developers for qualities listed in Section \ref{softwarequalities}. The interview questions are found in Appendix \ref{interviewquestions}.

\subsection{Surface Correctness and Verifiability}

@@

\subsection{Modifiability}

@@

\subsection{Traceability}

@@

\subsection{Reproducibility}

@@

\subsection{Unambiguity}

@@

This section answers the research questions listed in Section \ref{purpose} using the quantitative data presented in Section \ref{AHPresults}, qualitative data presented in Section \ref{interviewresults}, additional data from software package repositories and artifacts, and domain expert feedback. Each subsection answers one of the research questions. Software package artifacts are examined in Section \ref{artifacts}, tools are listed in Section \ref{tools}, development principles, processes, and methodologies are discussed in Section \ref{prinprocmeth}, development pain points are explored in Section \ref{painpoints}, and our recommendations for improving software qualities are presented in Section \ref{qualityrecommentations}. A comparison between our designations of the software packages to community rankings is made in Section \ref{comparison}. Finally, threats to the validity of this assessment are noted in Section \ref{threats}.
